---
title: "linear model of 1980s cars, I think"
author: "Jesse H"
date: "Fall 2026"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  

Form three regression models; 
  Model1 is mpg~disp, 
  Model2 is mpg~hp, and 
  Model3 is mpg~disp+hp. 
  
For each model find a 95% prediction interval of mpg given a value of 183 for disp  for GRIP and 250 for hp. 

After all three models have been constructed, compare Model1 with Model3 using anova. Document the comparison the markdown document, 

As usual, push the project up to your github account and submit the URL to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)
library(MASS)

```

```{r}
data(mtcars)
myData=mtcars

```

## Model 1 mpg ~ disp

### scatterplot


```{r}
plot(mpg~disp,data=mtcars, pch=18)
```
This scatterplot shows that displacement increases, mpg decreases.  
### Numerical results


```{r}
#mtcars$mpg
#mtcars$disp
cor(mtcars$mpg,mtcars$disp)
```
### Inferential  (Build model.2)
```{r}
model.1 <- lm(mpg~disp,data=mtcars)
summary.lm(model.1)
```
p value is significantly smaller.
#### predict model.2 at target point
```{r}
newdata=data.frame(disp=183,hp=250)
predict(model.1,newdata)
```

#### now add the model fit to our plot for model.2

```{r}
plot(mpg~hp,data=mtcars, pch=19)
```
This scatterplot shows that displacement increases, mpg decreases.
### Numerical results


```{r}
#mtcars$mpg
#mtcars$disp
cor(mtcars$hp,mtcars$disp)
```
### Inferential  (Build model.2)
```{r}
model.2 <- lm(mpg~hp,data=mtcars)
summary.lm(model.2)
```
```{r}
predict(model.2,newdata)
```
## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

`
  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## How do the models compare (Model.1 with model.2 in the anova results)?

